Calibration tests beyond classification

### 2021-03-17 paper/main.tex
Simplify subscripts
Add information about webpage to supplementary material

\begin{restatable}{lemma}{lemmaskceblock}\label{lemma:skceblock}
The block estimator of $\mathrm{SKCE}_k$ with
block size $B \in \{2,\ldots,n\}$, given by
\begin{equation*}
    \widehat{\mathrm{SKCE}}_{k,B} \coloneqq \bigg\lfloor \frac{n}{B} \bigg\rfloor^{-1} \sum_{b=1}^{\lfloor n / B \rfloor} \binom{B}{2}^{-1} \sum_{(b - 1) B + 1 \leq i < j \leq bB} h\big((P_{X_{i}}, Y_i), (P_{X_j}, Y_j)\big),
\end{equation*}
is an unbiased estimator of $\mathrm{SKCE}_k$.
\end{restatable}

@@

@@

For $b \in \{1, \ldots, \lfloor n / B \rfloor\}$, let
\begin{equation}\label{eq:etab}
    \widehat{\eta}_b \coloneqq \binom{B}{2}^{-1} \sum_{(b - 1) B + 1 \leq i < j \leq bB} h\big((P_{X_{i}}, Y_i), (P_{X_j}, Y_j)\big)
\end{equation}
be the estimator of the $b$th block. From \cref{lemma:hbound} it follows
that $\widehat{\eta}_b < \infty$ almost surely for all $b$.
Moreover, for all $b$, $\widehat{\eta}_b$ is a so-called U-statistic of
$\mathrm{SKCE}_k$ and hence satisfies
$\Exp \widehat{\eta}_b = \mathrm{SKCE}_k$~\citep[see, e.g.,][]{Vaart1998}.
Since $(P_{X_1}, Y_1), \ldots, (P_{X_n}, Y_n)$ are pairwise independent,
this implies that $\widehat{\mathrm{SKCE}}_{k,B}$ is an unbiased
estimator of $\mathrm{SKCE}_k$.
\end{proof}

>>>>

\begin{restatable}{lemma}{lemmaskceblock}\label{lemma:skceblock}
The block estimator of $\mathrm{SKCE}_k$ with
block size $B \in \{2,\ldots,n\}$, given by
\begin{equation*}
    \widehat{\mathrm{SKCE}}_{k,B} \coloneqq \bigg\lfloor \frac{n}{B} \bigg\rfloor^{-1} \sum_{b=1}^{\lfloor n / B \rfloor} \binom{B}{2}^{-1} \sum_{(b - 1) B < i < j \leq bB} h\big((P_{X_{i}}, Y_i), (P_{X_j}, Y_j)\big),
\end{equation*}
is an unbiased estimator of $\mathrm{SKCE}_k$.
\end{restatable}

@@

The source code of the experiments and instructions for reproducing the
results are available at
\url{https://github.com/devmotion/Calibration_ICLR2021}. Additional
material such as automatically generated HTML output and Jupyter
notebooks is available at
\url{https://devmotion.github.io/Calibration_ICLR2021/}.

@@

For $b \in \{1, \ldots, \lfloor n / B \rfloor\}$, let
\begin{equation}\label{eq:etab}
    \widehat{\eta}_b \coloneqq \binom{B}{2}^{-1} \sum_{(b - 1) B < i < j \leq bB} h\big((P_{X_{i}}, Y_i), (P_{X_j}, Y_j)\big)
\end{equation}
be the estimator of the $b$th block. From \cref{lemma:hbound} it follows
that $\widehat{\eta}_b < \infty$ almost surely for all $b$.
Moreover, for all $b$, $\widehat{\eta}_b$ is a so-called U-statistic of
$\mathrm{SKCE}_k$ and hence satisfies
$\Exp \widehat{\eta}_b = \mathrm{SKCE}_k$~\citep[see, e.g.,][]{Vaart1998}.
Since $(P_{X_1}, Y_1), \ldots, (P_{X_n}, Y_n)$ are pairwise independent,
this implies that $\widehat{\mathrm{SKCE}}_{k,B}$ is an unbiased
estimator of $\mathrm{SKCE}_k$.
\end{proof}
